\section{Affiliated Packages}
\label{sec:affil_package}

In order to foster collaboration, coordination, and code re-use, the \sunpyproj supports affiliated packages.
These are \python packages that build upon the functionality of \sunpypkg and/or provide general functionality useful to solar physics.
Affiliated packages can also be used to develop and mature subpackage functionality outside of the \sunpypkg core package for eventual inclusion.
The following requirements must be met by affiliated packages:
\begin{itemize}
    \item The package must make use of all appropriate features in \sunpypkg.
    \item Documentation must be provided that explains the function and use of the package, and should be of comparable quality to \sunpypkg documentation.
    \item A test suite must be provided to verify the correct operation of the package.
\end{itemize}
For a package to become affiliated, developers can apply to the lead developer, and the SunPy board provides the final approval.
Packages are re-reviewed on a yearly basis to ensure that they continue to meet the standards.
To aid discoverability, all affiliated packages are listed on the SunPy website,\footnote{\url{https://sunpy.org/team\#affiliated-packages}} and they are advertised at national and international conferences and workshops.
Finally, the development of these packages is provided informal support by the SunPy developer community, and
a package template\footnote{\url{https://github.com/sunpy/package-template}} has been developed that simplifies and standardizes packaging, testing, and documentation.

The following sections provide short descriptions of the existing affiliated packages.

\subsection{drms}
\label{sec:drms}

The \package{drms} \citep{Glogowski2019drms} package provides functionality to access data hosted by the JSOC.
Operated by Stanford University, JSOC is the primary data center for \textit{SDO} HMI, \textit{SDO} AIA, the Michelson Doppler Imager (MDI) on board the \textit{Solar and Heliospheric Observatory} (SOHO) instrument, and the Interface Region Imaging Spectrograph (IRIS).
JSOC's Data Record Management System (DRMS) is based on a PostgreSQL database that contains metadata, as well as pointers to image data, for every image contained in the archive.
The \package{drms} package enables querying the image metadata in the JSOC DRMS.
It can also be used to submit tailored data export requests (e.g., movies and images in various formats) and download data files.

\subsection{ndcube}
\label{sec:ndcube}

The \package{ndcube} package provides functionality for manipulating \textit{N}-dimensional coordinate-aware data.
Support is provided for any combination of axis types such as images (2 spatial axis), images over time (2 spatial and 1 time axis), spectrograms (wavelength and time), as well as more complex data sets (e.g., slit spectragraphs with wavelength, time, and spatial axes).
The package provides the \sunpycode{NDCube} class, a subclass of \astropy's \sunpycode{NDData} data container that holds together the data array, data uncertainties, and (potentially) a data mask.
\sunpycode{NDCube} enhances the functionality of \sunpycode{NDData} by adding support for handling coordinate transformations through the World Coordinate System (WCS) architecture commonly used in solar physics \citep{2002A&A...395.1061G, 2006A&A...449..791T}.
Powerful and intuitive tools are included for slicing datasets with a single command (using either array indices or coordinates) or slicing all components (including the data array and coordinates simultaneously).
This functionality enables users to manipulate their dataset quickly and accurately, allowing them to more efficiently and reliably achieve their science goals, and is meant to be used as a basis for more advanced and instrument-specific functionality (see \autoref{sec:irispy}).
Support for the generalized WCS module \citep{gwcs2018} is planned for the next major release.

\subsection{radiospectra}

The \package{radiospectra} package supports reading and analyzing dynamic radio spectra, as a function of time, primarily from e-Callisto, the International Network of Solar Radio Spectrometers\footnote{\url{http://www.e-callisto.org}}.
It provides tools for downloading and reading data, handling metadata, homogenizing data, and defining and subtracting background.
This package is planned to undergo major changes to use new tools being developed in \code{astropy/specutils}\footnote{\url{https://github.com/astropy/specutils}}.

\subsection{IRISPy}
\label{sec:irispy}

The \package{IRISPy} package provides tools to read, manipulate, and visualize data from IRIS \citep{DePontieu2014}.
IRIS is a NASA Small Explorer mission with two instruments: the Slit Jaw Imager (SJI) and a rastering slit spectrograph.
\package{IRISPy} is currently limited to reading level 2 data for either of these instruments.
This package provides data classes which hold data from SJI and the slit spectrograph.
Built on top of the functionality provided by \package{ndcube} (see \autoref{sec:ndcube}), \package{IRISPy} links the main observations, metadata, uncertainties, data unit, mask, and WCS transformations and provides easy slicing of the data in any axis.
Measurement uncertainties accounting for Poisson statistics and readout noise are automatically calculated, while a mask is used to ignore bad pixels when performing basic operations (e.g., mean, maximum, and visualizations).
