\acknowledgments

We thank the members of the community that have contributed to the \sunpyproj, that have opened issues and provided feedback, and have supported the project in a number of other ways.
Additionally, we thank Brian Dennis, Richard Schwartz, and Bill Thompson whose comments greatly improved this manuscript.

The following individuals recognize support for their personal contributions.
BMS is supported by the NSF grant AST-1715122 and acknowledges support from the DIRAC Institute in the Department of Astronomy at the University of Washington.
The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
DS was supported by STFC studentship ST/N504336/1 and STFC grant ST/N000692/1.

We acknowledge financial contributions from Google as part of the Google Summer of Code program and from the European Space Agency as part of the Summer of Code in Space program.
Additionally, we acknowledge current and future funding from the Solar Physics Division of the American Astronomical Society for SunPy workshops and tutorials at annual meetings.

This work has made use of data from the European Space Agency (ESA) mission \textit{Gaia}\footnote{\url{https://www.cosmos.esa.int/gaia}}, processed by the \textit{Gaia} Data Processing and Analysis Consortium (DPAC)\footnote{\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}}.
Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.

This research made use of \astropypkg,\footnote{\url{https://www.astropy.org}} a community-developed core Python package for Astronomy \citep{astropy2013, astropy2018}.

\software{
    \astropypkg \citep{astropy_v3.0.5},
    \package{astroquery} \citep{ginsburg_astroquery_2019},
    \package{drms} \citep{drms_v0.5.6},
    \package{GWCS} \citep{gwcs2018},
    \matplotlibpkg \citep{matplotlib_v3.1.0},
    \package{ndcube},
    \numpypkg \citep[v1.14.5][]{numpy},
    \pandaspkg \citep{pandas},
    \package{pfsspy} \citep{david_stansby_2019_3237053},
    \scipypkg \citep{scipy},
    \sunpypkg \citep{sunpy_v1.0.2}
}
